comgen-outline

### 2017-07-03 paper/comgen-paper.Rmd
some discussion of habituals endorsement expts and model results

>>>>

In Expt. 2b, we manipulated the event type (e.g., drinks coffee vs. beer) as well as the frequency with which a person has done the action in the past (e.g., three times in the past week vs. year) and measured the corresponding endorsements for habitual statements.
We saw tremendous flexibility in the frequency conditions that leads participants to endorse habituals.

Parallel to our analysis of generic statements, we articulated a number of alternative models and found that they were unable to explain the variability in endorsements. 
The regression model that uses the distinctiveness of the action (as measured in Expt. 2a) and the frequency of action is the best alternative model to explain endorsements. 
This model is not a predictive model, however; rather, it is a re-description of the data and helps us understand what the *predictive* RSA model is doing.

Distinctly from our case study on generic language, we manipulated rather than measured the target frequency (e.g., the frequency with which a person drinks coffee).
People are used to learning new information about others, and thus habitual language about people doing actions is particularly amenable to this kind of manipulation. 
By manipulating the target frequency, we have shown that it is causally related to habitual endorsements.
The relationship is not linear (or log-linear), however; habitual endorsements vary in complex ways that reflect listeners' prior knowledge about the event in the question and an underspecified threshold criterion.

This is particularly
